Operational adoption of new probabilistic point rainfall forecasts: the crucial role of a user-centric training

### 2021-01-22 manuscript/main.tex
Updates from Overleaf

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/UND_EFF_TradEPFs.png}}
\caption{Relationship between users' understanding (UND) of ensemble-based probabilistic forecasts and their effective (EFF) use in decision-making. Diagram's x-axis represents UND levels: "low", "medium", "high". Over time, training on ensemble-based probabilistic forecasts (cyan arrow in the x-axis direction) can push UND from "low" to "medium" or "high" levels. Diagram's y-axis represents EFF levels: "ineffective", "moderately effective", "very effective". Over time, training on how to communicate ensemble-based probabilistic outputs (cyan arrow in the y-axis direction) can push their effectiveness in decision-making from "ineffective" to "moderately effective" or "very effective". The green line represents optimal values for the UND-EFF relationship, and no UND-EFF pairs can exist in the green dashed area above the green line. Qualitatively, the blue line represents state-of-the-art UND-EFF relationship for traditional probabilistic ensemble-based forecasts.}
\label{UND_EFF_TradEPFs}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the real gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts (dashed fuchsia area) is greater than it was estimated at the beginning of the experiment as users with different ensemble-based forecasts understanding levels performed similarly in terms of effective use of such forecasts in decision-making processes.}
\label{UND_EFF_observed}
\end{figure}
"

>>>>

@@

\subsubsection{Products created for forecasters}
\begin{figure}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/.jpg}}
\caption{Panel (a) shows the climate regions of Costa Rica defined by IMN. Panels from (o-1) to (o-6) show 12-hourly rainfall observations between October 3rd and 5th, 2018. Panels from (i-1) to (i-3) show the impacts caused by the extreme event in the regions in which CNE declared the state of red alert (the photos come from www.teletica.com).}
\label{Fig5}
\end{figure}

\subsubsection{Subjective Verification}
